---
title: "Fitted Exponential Smoothing Model"
author: "BETS Package"
date: "`r Sys.Date()`"
output: html_document
params:
  ts: 21864
  alpha: !r NA
  beta: !r FALSE 
  gamma: !r FALSE
  additive: !r TRUE
  l.start: !r NULL 
  b.start: !r NULL
  s.start: !r NULL
  n.ahead: 10
  series.file: !r NA
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)

custom.ts = TRUE
ts = params$ts

if(class(ts) != 'ts'){
  custom.ts = FALSE
  code = as.integer(ts) 
} else{
  code = "None"
}

alpha = params$alpha
beta = params$beta
gamma = params$gamma
additive = params$additive
n.ahead = params$n.ahead
series.file = params$series.file

l.start = params$l.start
b.start = params$b.start
s.start = params$s.start


str = s.start
if(!is.null(s.start)){
  str = paste(s.start, collapse = ", ")
}
```

## User-Defined Parameters

 Parameter                          | Value              | Variable
 ---------------------------------- | -------------------| ----------
 Series code                        | `r code`           | `ts` 
 Alpha                              | `r alpha`          | `alpha` 
 Beta                               | `r beta`           | `beta` 
 Gamma                              | `r gamma`          | `gamma`
 Additive                           | `r additive`       | `additive`
 Level initial value                | `r l.start`        | `l.start` 
 Trend initial value                | `r b.start`        | `b.start` 
 Seasonal components initial values | `r str`            | `s.start` 
 Steps ahead                        | `r n.ahead`        | `n.ahead`
 
## Series Information

```{r echo = !custom.ts, eval = !custom.ts}
library(BETS)
info <- BETSsearch(code = ts, view = F)
```

```{r echo = FALSE, eval = custom.ts}
info <- data.frame(matrix(nrow = 1, ncol = 6))
names(info) <- c("Code","Description","Periodicity","Start","Source","Unit")
info[1,] <- c(code," ",frequency(ts),paste0(start(ts),collapse = "."),"Custom"," ")
```

```{r echo = FALSE, eval = !custom.ts}
names(info) <- c("Code","Description","Periodicity","Start","Source","Unit")
info[,"Start"] <- paste(start(ts),collapse=".")
info[,"Description"] <- trimws(info[,"Description"])
```

```{r echo = FALSE}
knitr::kable(info, format = "markdown")
```
 
## Graph

```{r eval = !custom.ts, echo = !custom.ts}
ts = BETSget(code = ts)
```


```{r}
library(mFilter)
trend = fitted(hpfilter(ts))


library(dygraphs)
dygraph(cbind(Series = ts, Trend = trend), main = as.character(info[1,"Description",])) %>%
  dySeries("Series",color = "royalblue",drawPoints = TRUE) %>%
     dySeries("Trend", strokeWidth = 1, strokePattern = "dashed", color = "red") %>%
        dyRangeSelector(strokeColor = "gray", fillColor = "gray") %>%
          dyAxis("y", label = info[1,"Unit"])
```

```{r echo = F}
# Aditivo e NAO TEM alpha
type1 = (additive && is.na(alpha))

# Aditivo e TEM alpha
type2 = (additive && !is.na(alpha))

# Multiplicativo e TEM alpha
type3 = (!additive && !is.na(alpha))

# Multiplicativo e NAO TEM alpha
type4 = (!additive && is.na(alpha))
```

## Smoothing

```{asis echo = type1}
You believe the series can be decomposed in a additive fashion (possibly because it seems homoscedastic) and you want the Holt-Winters R algorithm to choose the best alpha value. 
```

```{asis echo = type2}
You believe the series can be decomposed in a additive fashion (possibly because it seems homoscedastic) and you do not want the Holt-Winters R algorithm to choose the best alpha value. 
```

```{asis echo = type3}
You believe the series can be decomposed in a multiplicative fashion (possibly because it seems heteroscedastic) and you want the Holt-Winters R algorithm to choose the best alpha value. 
```

```{asis echo = type4}
You believe the series can be decomposed in a multiplicative fashion (possibly because it seems heteroscedastic) and you do not want the Holt-Winters R algorithm to choose the best alpha value. 
```

In addition, you `r if(!beta) 'do not'` want to model trend and `r if(!gamma) 'do not'` think the series has seasonal patterns.

Therefore, this is how we are going to create the model:

```{r echo = type1, eval = type1}
model = HoltWinters(ts, beta = beta, gamma = gamma,
                        l.start = l.start, b.start = b.start, s.start = s.start)
```

```{r echo = type2, eval = type2}
model = HoltWinters(ts, alpha = alpha, beta = beta, gamma = gamma,
                        l.start = l.start, b.start = b.start, s.start = s.start)
```

```{r echo = type3, eval = type3}
model = HoltWinters(ts, beta = beta, gamma = gamma, seasonal = "multiplicative",
                        l.start = l.start, b.start = b.start, s.start = s.start)
```

```{r echo = type4, eval = type4}
model = HoltWinters(ts, alpha = alpha, 
                    beta = beta, gamma = gamma, seasonal = "multiplicative",
                      l.start = l.start, b.start = b.start, s.start = s.start)
```

These are the final parameters:

```{r}
model
```

## Forecasts

```{r eval = custom.ts, echo = custom.ts}
library(BETS)
```

```{r}
preds = predict(model,h=n.ahead, main = as.character(info[,"Description"]), ylab = info[,"Unit"], style = "normal")
```

## Model Evaluation

If the model is well-specified, its normalized residuals should not surpass the boundaries of confidence intervals. In addition, it should look like white noise. Here, we plot the normalized residuals with a 95% confidence interval:

```{r}
std.resid = std_resid(model, alpha = 0.05)
```

We can use a Ljung-Box test to accept or reject the hypothesis of autocorrelation in the residuals (the forecasting errors):

```{r echo = -1}
bt = Box.test(preds$residuals, lag=20, type="Ljung-Box")
Box.test(preds$residuals, lag=20, type="Ljung-Box")
```

```{asis echo = bt$p.value < 0.5}
Note that the `p.value` is too low, which is an evidence of non-zero autocorrelations in the forecasting errors at lags 1 to 20. It suggests you should change the model specification.
```

```{asis echo = bt$p.value > 0.5}
Note that the `p.value` is high. So, there is little evidence of non-zero autocorrelations in the forecasting errors at lags 1 to 20.
```

To confirm these results, we can take look at the residuals ACF:

```{r}
corrgram(preds$residuals, lag.max = 20, mode = "bartlett", knit = T)
```

```{r echo = F, eval = !is.na(series.file)}
data = c(ts,preds$mean)

if(grepl("\\.spss$", series.file)){
  saveSpss(file.name = gsub("\\.spss$", "", series.file), data = data)
} else if(grepl("\\.dta$", series.file)){
  saveStata(file.name = gsub("\\.dta$", "", series.file), data = data)
} else if(grepl("\\.sas$", series.file)){
  saveSas(file.name = gsub("\\.sas$", "", series.file), data = data)
}else if(grepl("\\.csv$", series.file)) {
  write.csv(data, file = series.file, row.names = F)
} else if(grepl("\\.csv2$", series.file)) {
  series.file = gsub("\\.csv2$", ".csv", series.file)
  write.csv2(data, file = series.file, row.names = F)
}
```

<br>
`r if(!is.na(series.file)) 'The whole series and the model predictions are available at [THIS LINK]('``r if(!is.na(series.file)) series.file``r if(!is.na(series.file)) ')'`
